Output Summary

### 2021-01-05 03-post-process/output-plots.Rmd

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  scenario:
    label: "Scenario"
    value: "relate-hat-nat-age-4-5-same"
    input: text
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

```{r ocean-surv-plots, fig.width = 4, fig.height = 6}
par(mfrow = c(3,2), oma = c(1,1,0,0))
plot_tseries(post_summ(post, "phi_M_O1[.+,1]$"), main = "BON -> O1 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_M_O1[.+,2]$"), main = "BON -> O1 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = "O1 -> O2 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = "O1 -> O2 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$"), main = "O2 -> O3 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$"), main = "O2 -> O3 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Survival")
```

>>>>

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

```{r ocean-surv-plots, fig.width = 4, fig.height = 6}
par(mfrow = c(3,2), oma = c(1,1,0,0))
plot_tseries(post_summ(post, "phi_M_O1[.+,1]$"), main = "BON -> O1 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_M_O1[.+,2]$"), main = "BON -> O1 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = "O1 -> O2 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = "O1 -> O2 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = "O2 -> O3 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = "O2 -> O3 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Survival")
```
